Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
cutting repeteitive stuff

\section{Building Dataset}
\label{approach}

@@

\vspace{1ex}
\noindent\textbf{Social Factors} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile information:
%(\textit{https://github.com/\textbf{UserName}}). 
%

@@

Our data set~\cite{msr17challenge} is very diverse, consisting
of commits that date as far back as 2011. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014--2016).  Our intuition is
that the social attributes are less likely to have substantively changed over a
recent time span.

Since we are interested in the success of the job status of each contribution, we 
converted all Travis build statuses to two possible values:
\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
At this point 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\% if ran on the full data
set.

The high ratio of successful to unsuccessful builds leads a naive classifier to 
favor misclassifying unsuccessful builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of unsuccessful builds.  
We build this data set by copying over all unsuccessful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, a process known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.

>>>>

\section{Building the Dataset}
\label{approach}

@@

\vspace{1ex}
\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate thecommit web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline
%
We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile:
%(\textit{https://github.com/\textbf{UserName}}). 
%

@@

Our data set~\cite{msr17challenge} consists
of commits that date as far back as 2011. The social data we 
gather is recent, gathered in January 2017. To mitigate the threat of
using future results to predict previous events,
we removed only include data set commits from the years 2014--2016.  Our intuition is
that the social attributes are less likely to have substantively changed more recently.

Since we are interested in the success of the job status of each contribution, we 
converted all Travis build statuses to two possible values:
\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, we treat it as a failed build.

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We show results on both the 
downsampled and non-downsampled data sets.
